From Active Hostilities to Frozen Stalemates: Assessing the Role of External Support in Civil Conflict Dynamics

### 2023-10-23 paper.qmd
Add parameter and AME plots to manuscript

---
title: When Civil Conflicts Freeze
author: J.L.A. Krusell
date: "`r Sys.Date()`"
linestretch: 1.25
bibliography: library.bib
format: pdf
execute:
    echo: false
    warning: false
---

```{r setup, include = F}
library(bayesplot)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(knitr)

@@

theme_set(theme_tufte())
```

@@

```{r}
fit <- readRDS("./posteriors/probit.rds")

fit$draws("delta") |> mcmc_areas() +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction"))
```

@@

>>>>

---
title: "From Active Hostilities to Frozen Stalemates: Assessing the Role of External Support in Civil Conflict Dynamics"
author: J.L.A. Krusell
date: "`r Sys.Date()`"
linestretch: 1.25
bibliography: library.bib
format: pdf
execute:
    echo: false
    warning: false
---

```{r setup, include = F}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggdist)
library(latex2exp)
library(knitr)
library(patchwork)
library(tidyr)

@@

theme_set(theme_tufte(base_family = "TeX Gyre Pagella", base_size = 10))
```

@@

```{r}
#| fig.cap: Posterior estimates for \delta from a single variate probit model
fit <- readRDS("./posteriors/frozen-bin-all/model_output.rds")

delta <- fit$draws("delta", format = "df") |>
    select(matches("delta")) |>
    pivot_longer(everything(), names_to = "variable")

ggplot(delta, aes(x = value, y = variable, fill = variable)) +
    stat_halfeye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction"))
```

```{r}
#| fig.cap: Average marginal effects for the three treatment conditions on the predicted probability of a frozen conflict onset.[^ame]
ame <- fit$draws("ame", format = "df") |>
    select(matches("ame")) |>
    pivot_longer(everything(), names_to = "variable")

ggplot(ame, aes(x = value, y = variable, fill = variable)) +
    stat_eye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank()) +
    labs(x = parse(text = "bold('AME '*Delta)")) +
    scale_y_discrete(labels = c("ame[1]" = "Ext. Sup. Gov Only",
                                "ame[2]" = "Ext. Sup. Rebel Only",
                                "ame[3]" = "Ext. Sup. to Both")) +
    coord_flip()
```

[^ame]: Hello World

@@

::: {#refs}
:::

# Appendix

## Robust Checks

### Observational Probit Models

```{R}
#| fig-height: 7
dirs <- list.files("posteriors", full.names = T)

fits <- lapply(dirs, function(d) {
    names <- strsplit(basename(d), "-")[[1]]
    fit <- file.path(d, "model_output.rds") |> readRDS()

    fit$summary("delta", ~quantile(.x, probs = c(0.05, 0.1, 0.5, 0.9, 0.95))) |>
        rename(median = `50%`,
               lower90 = `5%`,
               upper90 = `95%`,
               lower80 = `10%`,
               upper80 = `90%`) |>
        mutate(outcome = names[1],
               treatment = names[2],
               episodes = names[3])
})

full.df <- bind_rows(fits) |>
    mutate(group = as.factor(outcome))

fn <- function(target) {
    sub.df <- filter(full.df, variable == target)
    ggplot(sub.df, aes(x = treatment, y = median, color = outcome)) +
        geom_point(size = 1.5, position = position_dodge(width = 0.25)) +
        geom_errorbar(aes(ymin = lower90, ymax = upper90), position = position_dodge(0.25), width = 0) +
        geom_errorbar(aes(ymin = lower80, ymax = upper80), position = position_dodge(0.25), size = 1.25, width = 0) +
        facet_grid(~episodes) +
        geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.2) +
        theme(axis.title.x = element_blank(),
              axis.title.y = element_blank())

}

p1 <- fn("delta[1]")
p2 <- fn("delta[2]")
p3 <- fn("delta[3]")

#    gov_delta <- lapply(fits, \(x) x[, 1]) |> do.call(cbind, args = _)
#reb_delta <- lapply(fits, \(x) x[, 2]) |> do.call(cbind, args = _)
#interaction_delta <- lapply(fits, \(x) x[, 3]) |> do.call(cbind, args = _)
#
#colnames(gov_delta) <- 1:ncol(gov_delta)
#p1 <- mcmc_intervals(gov_delta) + coord_flip()
#
#
#colnames(reb_delta) <- 1:ncol(reb_delta)
#p2 <- mcmc_intervals(reb_delta) + coord_flip()
#
#
#colnames(interaction_delta) <- 1:ncol(interaction_delta)
#p3 <- mcmc_intervals(interaction_delta) + coord_flip()

p1 / p2 / p3
```
